Exercise 1: Software Architecture Description of the HS07 System

### 2008-02-04 SAiP/Module1/H1/doc/paper.tex
Added figures to the document.

\author{
  Anders H Poder, Jesper Dalberg, Lars Kringelbach\\\\
  Department of Computer Science, University of Aarhus\\
  Aabogade 34, 8200 {\AA}rhus N, Denmark\\\\
  \makeatletter
  \texttt{<<Group name>>}\\
  \texttt{19951439, xxx, 20074842}\\
  \texttt{\{ahp, xxx, u074842\}@daimi.au.dk}
}

@@

$<<$Describe HS07 from this viewpoint using UML. Where appropriate
provide textual supplements$>>$

@@

$<<$Describe HS07 from this viewpoint using UML. Where appropriate
provide textual supplements$>>$

@@

$<<$Describe HS07 from this viewpoint using UML. Where appropriate
provide textual supplements$>>$

>>>>

\author{
  Anders H Poder, Jesper Dalberg, Lars Kringelbach\\\\
  Department of Computer Science, University of Aarhus\\
  Aabogade 34, 8200 {\AA}rhus N, Denmark\\\\
  \makeatletter
  \texttt{Group 11. Kilo}\\
  \texttt{19951439, 20074976, 20074842}\\
  \texttt{\{ahp, jdalberg, u074842\}@daimi.au.dk}
}

@@

The module viewpoint of the HS07 system.

\begin{figure}[!htb]
\center {\includegraphics[viewport=0 10 600 550,scale=0.4]{figures/mv.pdf}}
\caption{HS07 Package Diagram}
\label{fig:mv}
\end{figure}

The figure shows the packages of the HS07 system, and how they interact 
with java packages used.

@@

The Component \& Connecter view consists of an Active Objects diagram and a
sequence diagram. The Active Objects diagram shows the active objects of 
the HS07 system, and how they interact.

\begin{figure}[!htb]
\center {\includegraphics[viewport=0 10 600 420,scale=0.5]{figures/cc_ao.pdf}}
\caption{HS07 Active Objects}
\label{fig:cc_ao}
\end{figure}
The sequence diagram illustrates the timing of the interactions.
\begin{figure}[!htb]
\includegraphics[viewport=0 10 500 650,scale=0.3]{figures/sequence.pdf}
\caption{HS07 Sequence Diagram}
\label{fig:sequence}
\end{figure}

@@

The allocation viewpoint illustrates how components are deployed im actaual processes
within the HS07 system.

\begin{figure}[!htb]
\center {\includegraphics[viewport=0 10 700 350,scale=0.4]{figures/deployment.pdf}}
\caption{HS07 Allocation Diagram}
\label{fig:allocation}
\end{figure}
